---
title: "EDALA1"
author: "SUPRIYA_SUCHITHRA"
date: '2022-06-23'
output:
  pdf_document: default
  html_document: default
---

```{r }
value<-read.csv(file.choose(),sep=',',header=TRUE);

```
This is to read the csv file and store it in value. This is used when data is too large.
```{r}
value
```
Display the contents of value. All observations and variables.
```{r}
   summary(value); 
```
Summary of the dataframe
```{r}
  str(value);
```
Structure of dataframe. str() commands is used to examine the structure of the object. also gives the number of observations and number of variables along with data types.
```{r}
   value; 
```
```{r}
   class(value); 
```
class() command is used to obtain information about the type of object.
```{r}
   history(value); 
```
```{r}
   value1<-as.factor(value$Country.name);
```
Here, Country.name is Character. as.factor() command converts character to factor data type. and stores in value1 object.
```{r}
   value1; 
```
we are printing the entries of value1 object.
```{r}
  value2<-as.numeric(value1);
```
value1 object's data type is factor and we are converting factor to numeric.
```{r}
   value2;
```
Displaying the values in value2 object.
```{r}
   as.factor(value2); 
```
Converting numeric values back to factor values.
```{r}
   value[1]; 
```
Prints the first column in value object.
```{r}
   value[3]; 
```
Prints the thrid column in value object.
```{r}
   value[1:3]; 
```
Prints the first three columns of dataframe value.
```{r}
   value[-1]; 
```
Prints all columns except first column of value dataframe.
```{r}
   value[c(1,3,4,8)]; 
```
Prints only the selected columns and all rows in value dataframe.
```{r}
   value[value>5]; 
```
```{r}
   length(value); 
```
Prints total columns in dataframe value.
```{r}
   value[(length(value)-2):length(value)];
```
```{r}
   max(value$lowerwhisker); 
```
Prints the maximum value in column lowerwhister in value dataframe.
```{r}
   max(value$Country.name); 
```
Prints the maximum value in column Country.name in value dataframe.
```{r}
   min(value$lowerwhisker); 
```
Prints the minimum value in column lowerwhister in value dataframe.
```{r}
   max(value$Regional.indicator); 
```
Prints the maximum value in column Regional.indicator in value dataframe.
```{r}
   which(value==max(value$Country.name)); 
```
```{r}
   value[seq(1,length(value),5)]; 
```
The seq R function generates a sequence of numeric values.
```{r}
  sort(value$Country.name); 
```
sort function returns the results sorted in ascending order. we can use a minus sign to get results in descending order.
```{r}
  sort(value$Standard.error.of.ladder.score); 
```
```{r}
  sort(value$Social.support); 
```
```{r}
  order(value$Country.name); 
```
order function in R returns the position of each element of its input in ascending or descending order.
```{r}
  order(value$Standard.error.of.ladder.score); 
```
```{r}
  sort(value$Social.support); 
```
```{r}
  rank(value$Country.name); 
```
rank function will return a dataframe providing the rank of each element within a dataframe.
```{r}
  rank(value$Standard.error.of.ladder.score); 
```
```{r}
  rank(value$Social.support); 
```
```{r}
  value[3,3]; 
```
Prints the value present in thrid row, thrid column in value dataframe.
```{r}
  value[3,1:4]; 
```
Prints the value in thrid row of all four columns in value dataframe.
```{r}
  value[,3]; 
```
Prints values of all rows in thrid column.
```{r}
  value[c(1,3,5,7),-4]; 
```
Only the specified rows and all columns except fourth column will be printed.
```{r}
  value[c(1,3,5,7),"Social.support"];
```
here the column name is specified as "Social.support", only that column's specified rows will be printed.
```{r}
  value[3]; 
```
all rows of column three will be printed.
```{r}
  value[c(1,100),]; 
```
All column values of specified rows will be printed.
```{r}
  order(value$upperwhisker,value[,2]); 
```
we are using order function on upperwhisker column.
```{r}
  with(value,order(value$upperwhisker,value$Social.support));
```
the with function evaluates an R expression in an environment constructed based on data frame.
```{r}
  value$lowerwhisker; 
```
Prints all rows of lowerwhisker column.
```{r}
  value$Regional.indicator; 
```
prints all rows of Regional.indicator column.
```{r}
  value$Regional.indicator[1:4]; 
```
prints only the first four rows of Regional.indicator column.
```{r}
  value[,'Regional.indicator']; 
```
prints all rows of Regional.indicator column.
```{r}
  search(); 
```
shows all the libraries which are loaded to memory.
```{r}
  with(value,Regional.indicator); 
```
the with function evaluates an R expression in an environment constructed based on data frame. prints all values in Regional.indicator column.
```{r}
  with(value,upperwhisker); 
```
the with function evaluates an R expression in an environment constructed based on data frame. prints all values in upperwhisker column.
```{r}
head(value);
```
the head() function in R returns the first part of a vector,matrix,table,data frame or function that is passed to it as a parameter. generally, it returns first six values.
```{r}
  tail(value);
```
the tail() function in R returns the last part of a vector,matrix,table,data frame or function that is passed to it as a parameter. generally, it returns last six values.
```{r}
head(value,n=10);
```
head() returns first part of data frame. generally, it returns first six rows. but, here we are externally specifing that first ten rows must be printed.
```{r}
  summary(value);
```
```{r}
  names(value) 
```
gives all the column names of data frame value.
```{r}
  row.names(value); 
```
gives only row names of data frame value.
```{r}
  colnames(value); 
```
gives only column names of data frame value.
```{r}
  dimnames(value); 
```
gives both row and column names of data frame value.
```{r}
  value4.mat=as.matrix(value);
value4.mat;
```
here we are converting data frame to matrix and printing it.
```{r}
  value5.list=as.list(value);
value5.list;
```
here we are converting data frame to list and printing it.
```{r}
  mean(value$upperwhisker);
```
printing the mean of column upperwhisker of value data frame.
```{r}
  mean(value$Ladder.score);
```
printing the mean of column Ladder.score of value data frame.
```{r}
  min(value$upperwhisker);
```
printing the minimum value of column upperwhisker of value data frame.
```{r}
  min(value$Ladder.score);
```
printing the minimum value of column Ladder.score of value data frame.
```{r}
  max(value$upperwhisker);
```
printing the maximum value of column upperwhisker of value data frame.
```{r}
  max(value$Ladder.score);
```
printing the maximum value of column Ladder.score of value data frame.
```{r}
  length(value$upperwhisker);
```
printing the total entries of column upperwhisker of value data frame.
```{r}
  sd(value$upperwhisker);
```
printing the standard deviation value of column upperwhisker of value data frame.
```{r}
  sd(value$Ladder.score);
```
printing the standard deviation value of column Ladder.score of value data frame.
```{r}
  log(value$Ladder.score);
```
the log() function returns the logarithm of the value in the base. by default, this function produces a natural logarithm of the value.
```{r}
  quantile(value$Ladder.score);
```
the quantile() function in R can be used to calculate sample quantiles of the dataset.
```{r}
  fivenum(value$Ladder.score);
```
to calculate the five-number summary in the R programming language, we use fivenum() function.
```{r}
  quantile(value$Ladder.score,0.2);
```
calculate quantile at 20%.
```{r}
  quantile(value$Ladder.score,c(0.2,0.5,0.8));
```
calculating quantiles at 20%,50% and 80%.
```{r}
  quantile(value$Ladder.score,c(0.5,0.75,0.25));
```
calculating quantiles at 50%,75% and 25%.
```{r}
  cumsum(value$Ladder.score);
```
gives cummulative sum of Ladder.score column.
```{r}
  cummax(value$Ladder.score);
```
gives cummulative maximum values of Ladder.score column.
```{r}
  cummin(value$Ladder.score);
```
gives cummulative minimum values of Ladder.score column.
```{r}
  cumprod(value$Ladder.score);
```
gives cummulative product values of Ladder.score column.
```{r}
  seq(along=value);
```
```{r}
  seq_along(value);
```
```{r}
  seq(from=1,to=10,by=2);
```
```{r}
  colMeans(value$Ladder.score);
```
```{r}
  library(dplyr);
value %>% mutate(newcol=1);
```
Loading library dplyr. and adding new column to the value data frame. we use mutate function to add new column.
```{r}
  value %>% select(-Logged.GDP.per.capita);
```
we are deleting the existing column from value data frame for that we use select function.
```{r}
  value %>% select(Ladder.score,everything());
```
for reordering we use select function. here, we are selecting Ladder.score to be first column and everything function to specify that other columns will be intact.
```{r}
value %>% filter(Country.name=="New Zealand" & Ladder.score>=6.965	& Ladder.score<=7.277);
```
selecting only Country.name as New Zealand.
```{r}
value %>% filter(Country.name=="New Zealand" & Ladder.score>=6.965	& Ladder.score<=7.277) %>% select(Country.name,Ladder.score);
```
along with selecting country name we are displaying only country name and ladder score columns.
```{r}
value %>% rename(Country=Country.name);
```
renaming the existing column name. for that we use rename function.
```{r}
with(value,table(upperwhisker,Ladder.score));
```

```{r}
value6=xtabs(upperwhisker~Ladder.score+lowerwhisker);
value6;
```
the xtabs() function in R allows you to quickly calculate frequencies for one or more variables.
```{r}
library(ggplot2);
ggplot(value,aes(x=Ladder.score, y=upperwhisker))+geom_point();
```
visualization of points.
```{r}
ggplot(value,aes(x=Ladder.score, y=upperwhisker))+geom_point();
```
```{r}
library(dplyr);
vec<-rep(c(2),149);
value %>% mutate(newcol1=vec);
```
```{r}
library(ggplot2);
ggplot(value,aes(x=Ladder.score, y=upperwhisker))+geom_line();
```
visualization of line graph.
```{r}
ggplot(value,aes(x=Ladder.score, y=upperwhisker))+geom_line()+geom_point();
```
visualization of points on line graph.
```{r}
ggplot(value,aes(x=Ladder.score, y=upperwhisker))+geom_col();
```
visualization of bar graph of values.
```{r}
ggplot(value,aes(x=Ladder.score))+geom_bar();
```
visualization of bar graph of counts.
```{r}
ggplot(value,aes(x=Ladder.score))+geom_histogram();
```
visualization of histograms.
```{r}
ggplot(value,aes(x=Ladder.score))+geom_histogram(binwidth=4);
```
```{r}
ggplot(value,aes(x=Ladder.score, y=upperwhisker))+geom_boxplot();
```
visualization of box plot.